Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
mejore las conclusiones

In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored. This phenomenon occurs because increasing the stiffness level promotes the repulsion between pedestrians pair interactions. As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap between pedestrians and the contacts among them. The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which leads to a more efficient evacuation dynamics. \\

@@

Regarding the parameters of the model, we found that it is possible to reduce the original SFM parameters to three dimensionless parameters. The original parameters interrelate to each other through the dimensionless ones. Many different settings can produce the same dimensionless parameters. Thus, no univocal relations can be established between the individualistic parameters and collective dynamics. In order to explore the outcomes from different dimensionless numbers, we compared numerical results with empirical measurements. We found good candidates to reproduce the qualitative behavior of empirical measurements in the range and $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$. Nevertheless, this is a first sketch to arrive at a set of dimensionless parameters that may be suitable to reproduce empirical measurements. We encourage further research that seeks to find the values of the dimensionless numbers that can reproduce experimental data.\\

>>>>

In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored. This phenomenon occurs because increasing the stiffness level promotes the repulsion between pedestrians pair interactions. As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap between pedestrians and the contacts among them. The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exit (blocking cluster), which leads to a more efficient evacuation dynamics. \\

@@

Regarding the parameters of the model, we found that it is possible to reduce the original SFM parameters to three dimensionless parameters. The original parameters interrelate to each other through the dimensionless ones. Many different settings can produce the same dimensionless parameters. Thus, no univocal relations can be established between the individualistic parameters and collective dynamics. In order to explore the outcomes from different dimensionless numbers, we compared numerical results with empirical measurements. We found good candidates to reproduce the qualitative behavior of empirical measurements in the range $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$. Nevertheless, this is a first sketch to arrive at a set of dimensionless parameters that may be suitable to reproduce empirical measurements. We encourage further research that seeks to find values of the dimensionless numbers that best reproduce experimental data.\\
